---
title: "Project For Applied linear regression"
author: "Maxime Cathala"
date: "11/4/2022"
output: pdf_document
---

# Loading Data
```{r}
library("faraway")
path <- "/Users/Maxime/Desktop/NBA_Salaries/2017-18_NBA_salary.csv"
full_df <- read.csv(path, header=TRUE, stringsAsFactors=FALSE)
nba <- subset(full_df, select = c(Salary,MP,TS.,X3PAr,FTr,TRB.,AST.,STL.,
                                     BLK.,TOV.,USG.))
nba <- na.omit(nba)
head(nba)
```

## Full Model Ana
### Create Full Model (No modif, All predictors vs Salary)
```{r}
full <- lm(Salary ~ .,data = nba)
```

### Model Assumptions:

|   Residuals vs Fitted:
|       Quite a random scatter.
|          If not looking where no points are below


```{r}
plot(full, which = 1)
```

|   Normality:
|     Pb with the higher quantiles
|         Points should follow the line (Normal distribution)
```{r}
plot(full, which = 2)
```


## Variable selection (AIC-Methods on Full Model)

```{r}
full_AIC <- step(full, direction = "backward",k = 2)
```
### Fit Reduced model with selected predictors in AIC
```{r}
reduced <- lm(Salary ~ AST. + USG. + TRB. + MP, data = nba)
summary(reduced)
vif(reduced)
```

### Is reduced model better or same then full?
The hypotheses for the F-test performed in the anova are: 

|  H0: The additional terms in the full model are 0. 
|  HA: At least one of the additional terms is non 0.
|       Yes: p val = 0.9577
```{r}
anova(reduced, full)
```

# Exploring other methods Full with sqrt(response)
## Remove outliers (Salary over 25millions)
```{r}
nba2 <- nba[nba$Salary <= 25000000,]
full2 <- lm((Salary) ~ .,data = nba2)
full2_AIC <- step(full2, direction = "backward",k = 2)
reduced2 <- lm(Salary ~ USG. +  TRB. + MP,data = nba2)
anova(reduced2,full2)
```

### Full with sqrt(response)
```{r}
full3 <- lm(sqrt(Salary) ~ .,data = nba)
full3_AIC <- step(full3, direction = "backward",k = 2)
reduced3 <- lm(sqrt(Salary) ~ AST. + USG. + TRB. + MP,data = nba)
summary(reduced3)
```


# Reduced models from both methods
```{r}
summary(reduced3)
summary(reduced2)
```

### Is reduced model better or same then full?
The hypotheses for the F-test performed in the anova are: 

|  H0: The additional terms in the full model are 0. 
|  HA: At least one of the additional terms is non 0.
|       Yes: p val = 0.9788
```{r}
anova(reduced3,full3)
```

